\sysfull

### 2018-08-05 paper/asplos19/paging.tex
first pass over paging

(Step 7). \sys keeps track of the page tags for

@@

{\tt \underline{store}} (Step 4).

@@

locations in the main memory \texttt{\underline{private}}. If a task were allowed
to (re-)execute after only some pages have been committed to
\texttt{\underline{store}}, the task might see protected variables in an
inconsistent state; \sys's two-phase commit prevents this inconsistency. \\

@@

commits pages from \texttt{\underline{shadow}} to \texttt{\underline{store}}

@@

and the execution restarts from the most recently committed point (i.e., from
the first task in a coalesced sequence of tasks). If power fails in the second

@@

commit and \sys clears the counter when commit completes (Line 14).  The

@@

11) and \sys clears the index at the end of the phase (Line 15).

@@

\sys's implementation is also efficient because the memory manager does not
copy from \texttt{\underline{shadow}} to \texttt{\underline{store}}, instead

@@

modifications to protected data do not affect their original memory locations,

@@

failure erases the contents of the page buffer, preventing a re-executing task
from observing updates in the page buffer from a previous execution attempt.

@@

correctly access their original memory locations in \texttt{\underline{store}}.
\sys assumes that the write to a non-volatile word in memory is atomic. \\

@@

check on every read and write. An alternative approach~\cite{alpaca} relied on a compiler to analyze memory operations and try to insert memory protection code mostly at the beginning of a task, leaving most
memory accesses uninstrumented.\\

@@

scheme brings several benefits over a static approach.  First, the limitations
of static analysis preclude some uses of pointers due to potential pointer

>>>>

(Step 7). The VMM keeps track of the page tags for

@@

{\tt \underline{private}} (Step 4).

@@

locations in the main memory \texttt{\underline{private}}.\\

@@

commits pages from \texttt{\underline{shadow}} to \texttt{\underline{private}}

@@

and the execution restarts from the most recently committed point (i.e., from the beginning of a coalesced task). If power fails in the second

@@

commit and the VMM clears the counter when commit completes (Line 14).  The

@@

11) and the VMM clears the index at the end of the phase (Line 15).

@@

\sys's implementation is also efficient because the VMM does not
copy from \texttt{\underline{shadow}} to \texttt{\underline{private}}, instead

@@

modifications to protected data do not affect the \texttt{\underline{private}} buffer,

@@

failure erases the contents of the \texttt{working} buffer, preventing a re-executing task
from observing updates from a previous execution attempt.

@@

correctly access their original memory locations in \texttt{\underline{private}}.\\

@@

check on every read and write. 

@@

scheme brings several benefits over a static approach (i.e.~\cite{alpaca}).  
First, the limitations of static analysis preclude some uses of pointers due to potential pointer
